The effect of detector nonlinearity on \wfa\ PSF profiles for weak gravitational lensing measurements

### 2016-05-17 ms.tex
Response to refree report

\documentclass[11pt,preprint,flushrt]{aastex}
%\usepackage{natbib}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{latexsym}
\usepackage{cancel}
\usepackage{verbatim}
\usepackage{indentfirst}
\usepackage{multirow}
\usepackage{color}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{graphicx}

@@

\section{Introduction}
Weak gravitational lensing (WL) has been identified as a powerful probe of the nature and evolution of the components of the Universe. In particular, \emph{cosmic shear}\textemdash the subtle  distortions of background galaxy shapes by the large-scale structure of the Universe\textemdash constrains the properties of dark matter and dark energy through the measurement of the expansion history and growth of structure of the Universe \citep{refregier03, hoekstra08, kilbinger15}. WL measurements also allow to test the validity of General Relativity that relates the gravitational potential to the matter-energy distribution. Several surveys in the visible part of the spectrum  of $>1000$~deg$^2$ of the sky are currently underway and use the WL signal from hundreds of millions of galaxies as one of their central scientific techniques (\emph{e.g.}, the Dark Energy Survey (DES), \citealt{diehl12}, \citealt{jarvis15}; the Kilo-Degree Survey (KiDS), \citealt{kuijken15}; and the Hyper Suprime-Cam Survey (HSC), \citealt{miyazaki12}). In addition, future ground- and space-based surveys and missions in the visible and near infra-red (NIR) are planned to image more than O($10^9$) galaxies in the next decade (\emph{e.g.}, the Large Synoptic Survey Telescope (LSST), \citealt{ivezic08}; the Euclid spacecraft, \citealt{laureijs11}; and NASA's Wide-Field Infrared Survey Telescope (WFIRST), \citealt{green12}, \citealt{spergel13}, \citealt{spergel15}).

The process of extracting the WL signal from images of the sky, in the presence of intrinsic galaxy ellipticity variations that are $\sim$ 0.4 r.m.s, is highly non-trivial. It must be done through a statistical analysis of large galaxy samples, with a careful control of systematic uncertainties. The dominant signal produced by WL can be described by a local linear transformation of the source image that produces a shear (a complex, spin-2 field of components $\gamma_1$ and $\gamma_2$) and a scalar magnification, both of which have an r.m.s. amplitude of only $\sim 2 \%$ in the case of cosmic shear. Most of the background galaxies usable by WL are at hight redshift (with low signal-to-noise (S/N) ratio) and with a size comparable or smaller than the Point Spread Function (PSF) of the imaging system. Incorrect estimation of the size of the PSF induces a modulation in the signal (multiplicative errors), and errors in the estimation of the PSF ellipticity propagate into asymmetries that produce coherent spurious patterns (additive errors) that mimic the WL signal. Bright stars are commonly used to estimate the PSF, and then this information must be interpolated to the observed galaxy positions to deconvolve the PSF contribution and measure the galaxy shape (in the form of a complex ellipticity $e=e_1 + i e_2$) to estimate the shear field.\footnote{Most of the shape measurement algorithms to date rely on the accurate measurements of galaxy shapes to produce an estimator of the WL shear field $(\gamma_1, \gamma_2)$. However, recent algorithms propose skipping this step and creating a direct shear estimator through Bayesian analysis (\citealt{bernstein14}, \citealt{bernstein15}, \citealt{schneider15}).} This interpolation step introduces systematic errors if the information inferred from the stars does not fully constrain the PSF at the galaxy position with the required accuracy. In order not to bias the determination of dark energy and other cosmological parameters in Stage IV surveys (in the language of \citealt{albrecht06}), the ellipticity and relative size of the PSF must be known to an accuracy of O(10$^{-3}$) (\citealt{huterer06}, \citealt{amara08}, \citealt{paulin08}, \citealt{paulin09}, \citealt{massey13}, \citealt{cropper13}) or better ($4.7 \times 10^{-4}$ for the knowledge of the \wfa\ PSF ellipticity, \citealt{spergel13}).

@@

Systematic errors that originate from a telescope's detectors (image sensors) introduce biases in astronomical observables such as photometry and astrometry that propagate into shear measurement biases. These type of errors have been extensively studied in the case of thick, fully-depleted, high-resistivity Charge Coupled-Devices (CCDs), which are the detectors of choice for many current and planned surveys such as DES, HSC, and LSST (\citealt{stubbs14}, \citealt{plazas14}, \citealt{gruen15}). It is of great importance to quantify the impact of these sensor effects on the inference of cosmological parameters, in particular through WL (\citealt{jarvis14}, \citealt{mandelbaum14b}, \citealt{meyers14}). Future missions such as the James Webb Space Telescope and \wfa\ will utilize a family of near-infrared detectors that are also subject to effects such as nonlinearity, reciprocity failure (\citealt{bohlin05}, \citealt{biesiadzinski11}), interpixel capacitance (IPC; \citealt{mccullough08}, \citealt{kannawadi15}), and persistence (\citealt{smith08}). These effects can imprint biases on weak lensing shape measurements if not taken into account.

@@

The detector arrays are fabricated with a hybrid complementary metal-oxide-semiconductor (CMOS) architecture, which combines the qualities of HgCdTe to detect infra-red light (\emph{e.g.}, altering the relative molar contributions of mercury and cadmium allows one to tune the band gap up to an order of magnitude) and the advanced readout performance of integrated circuits. Light is absorbed, converted to charge through the photoelectric effect, and collected by electric fields generated by a reverse-biased p-n junction in the detector layer.  The charge per pixel is then converted to a voltage and amplified through a source follower. This operation is performed in the silicon readout integrated circuit (ROIC) layer, which is connected to the HgCdTe detection layer by indium interconnects (one indium bump per pixel). Finally, the ROIC transfers the signal (and for this it is also known as ``multiplexer") to the off-chip electronics at the edge of the FPA, where it is digitized through analog-to-digital converters \citep{beletic08}.

@@

Assuming that the dominant contribution to nonlinearity is the varying capacitance of the pixel p-n junction, the correction to the detector signal is well approximated by a quadratic term:
\begin{align}
S(Q)= Q - \beta Q ^2
\label{NL}
\end{align}
Here, $Q$ is the true number of elementary charges collected in the pixel, $S$ is the number inferred from the voltage change at the sense node, and $\beta$ is a constant.  To estimate $\beta$, we compute $Q(V)=C(V)*V/q_e$, where $q_e$ is the elementary charge, and the total capacitance is given by the varying junction capacitance plus a constant $C(V) = C_{\rm jn}(V) + C_{\rm fix}$. The junction capacitance varies as (\citealt{mccaughrean87})
\begin{equation}
C_{\rm jn}(V) \propto (1+V/V_{bi})^{-1/2} \;.
\end{equation}
Here, $V_{bi}$ is the ``built in'' potential of the junction and $V=V_{\rm DSUB}-V_{\rm RESET}+\delta V$, where $V_{\rm DSUB}$ is the constant potential at the diode cathode, $V_{\rm RESET}$ is the initial potential at the anode, and $\delta V$ is the change in anode potential due to accumulated photocharge.  As an example, we plug in measurements of a 2.4$\mu$m cutoff H2RG by Finger 2006:\footnote{\url{https://www.eso.org/sci/meetings/2006/neon-2006/Finger.pdf}}
\begin{eqnarray*}
V_{\rm bi} &=& 0.412\ {\mbox V} \\
V_{\rm DSUB} &=& 1\ {\mbox V} \\
V_{\rm RESET} &=& 0.5\ {\mbox V} \\
C_{\rm fix} &=& 17.8\ {\mbox fF} \\
C_{\rm jn}(V=.912\ {\mbox V}) &=& 30\ {\mbox fF}
\end{eqnarray*}
Using these parameters to compute $Q(V)$ for $ 0\le \delta V \le 0.3$ V (corresponding to maximum $Q$=60115) and then inverting to find $S(Q)$, we find it is well-fit (to 0.1\% or better) by Eq. \ref{NL} with $\beta=1.18 \times 10^{-6}$. In practice, HXRG calibrations have included additional polynomial parameters which can reduce residuals, extend the range of valid $Q$, and account for additional nonlinear effects (\citealt{hilbert04}, \citealt{hilbert08}, \citealt{hilbert14}); however, the additional parameters are highly degenerate, resulting in large variances in the fitted values.  For our purposes, it suffices to analyze the shape-distorting effects of nonlinearity using a single parameter, $\beta$, which encapsulates most of the effect. In this paper we chose a nominal value of $\beta_0=5\times 10^{-7}$, which is near the midpoint of the measured range for $\beta$ in \citealt{hilbert14}.

@@

\citet{kannawadi15} have developed within \gs\ v1.3 a \wfa\ module called ``{\tt{galsim.\\ wfirst}}", which allows the simulation of a PSF profile according to the optical design characteristics of the \wfa\ WFI \citep{pasquale14}\footnote{\citealt{pasquale14} discuss the so-called ``Cycle 4" optical design, whereas the \gs\ \wfa\ module\textemdash used in this work\textemdash uses files corresponding to ``Cycle 5".} through the calling of the {\tt{galsim.wfirst.getPSF}} routine. 
This routine returns a {\tt{python}} dictionary indexed by each one of the 18 H4RG detectors of the FPA. It uses the optical configuration of the pupil plane\footnote{The pupil plane configuration is not circular in all the bands but the simulated PSFs use circular apertures.} to simulate PSF images in any \wfa\ WFI bandpass filter, with expected optical aberrations approximated as a linear combination of Zernike polynomials (up to Noll order equal to $11$, \citealt{noll67}). For this work, we have created simulations in the four bands of the HLS.  A central circular obscuration ($30 \%$) and six support struts are included as well. The pupil plane configurations and Zernike models are publicly available.\footnote{\url{http://wfirst.gsfc.nasa.gov/science/sdt_public/wps/references/instrument/}}

The current version of the module does not include PSF variations across the detector field of view, and the PSF returned corresponds to that at each detector center. In addition, the module assumes that the pupil plane configuration of all the six bands is the same and equivalent to that of the ``red" bands (\emph{i.e.}, W149, H158, and F184), and that the struts are not, in general, radial nor evenly spaced. 
The module generates PSF models that do not include pointing jitter nor charge diffusion. These effects could be added to the profile (\emph{e.g.,} by means of an extra convolution with a Gaussian profile in the case of diffusion), but we did not include them in our simulations. Their effect would be to create a slightly larger PSF, reducing the impact NL. Their omission makes our results slightly conservative.

@@

Note that the NL effect on the reconstructed image from dithering real exposures will depend on the centroid of the source in the dithered inputs: an exposure where the PSF peaks at a pixel center will have higher NL than an exposure where the peak is spread more evenly over 2-4 pixels.  To mimic this behavior in our approximation, we randomly offset our PSF centroids 100 times uniformly over a box the size of a native detector pixel, and we average all shape measurements over these realizations.  With $N$=3, the variation of the NL correction in the pixels of the oversampled image should be similar to the variations in the 5-8 exposures combined using the WFIRST dither strategy.  In practice, we find that the scatters of the shape measurements over these realizations are negligible relative to the means.

@@

Notice that this method to approximate oversampled images can only be used in the case of sensor effects such as NL, which only depend on each pixel individually. In the case of other effects that correlate the signal in one pixel with the signal of its neighbors (such as IPC), the effect should be applied to the native scale of the detector and then a properly sampled image should be generated through adequate combination of several dithered images before performing any analysis (see for instance the ``interleaving" algorithm of \citealt{kannawadi15}, also included in \gs).

\begin{figure}[!ht]
\centering
\resizebox{\hsize}{!}{\includegraphics[page=1]{plots/f1.eps}}
\caption{Example of the \wfa\ PSF profiles in the Y106 band created by the {\tt{galsim.wfirst.getPSF}} method. The profile is drawn on a postage stamp with a size of $1.5k \times1.5k$ pixels ($k=64$) and a resolution of $p/N$, with $p=0.11$ arcseconds and $N=3$. Before drawing the profiles, they are first convolved with a pixel response of size $p$ and given a flux obtained through the use of the {\tt{galsim.wfirst.getBandpasses (AB\char`_zeropoint=True)}} routine at an AB magnitude of 18.3 (at an exposure time of 168.1 seconds). However, to preserve the correct response to NL, the higher-resolution image has $N^2$ more total flux. The NL effect is applied at the high-resolution pixel scale $p/N$, but the centroid of the profile is randomized within the native pixel scale $p$ (in this example the centroid and the pixel center coincide). The upper left panel shows the full postage stamp PSF image without the NL applied, while the lower left panel shows a zoom into the core (squared central region in upper left panel) of 30 by 30 high-resolution pixels. The right-hand side image shows the fractional difference between the PSF without the NL applied and a PSF with NL using $\beta_0$ for the model parameter.} 
\label{f1}
\end{figure}

@@

Total and peak flux values at each filter per postage stamp are shown in Table 1. The brightest magnitude used was AB $m=18.3$, based on the peak value of the PSF profile in the Y106 band when rendered into a postage stamp at the native pixel scale and placed at the center of the pixel: $\sim 1.00237\times10^{5}$ electrons, representing about $90\%$ of the typical full well depth in the pixels of the H4RG detectors\textemdash$\ \sim1.1\times10^{5}$ electrons. Note that this peak value is an upper limit and will vary for a slightly offset profile. For our calculations, we randomize the centroid of the profile within the native scale pixel. In addition, since NL is a function of signal, and since \gs\ conserves total flux when changing pixel scales, the total flux in the higher resolution image must be multiplied by a factor of $N^2$ to preserve the appropriate response per pixel to this effect, correcting for the fact that the new image has a factor of $N^2$ more pixels than the one created at the native scale.

@@

The basic simulation process is summarized by the following steps:  
\begin{itemize}
\item[1.] Create a \wfa\ PSF surface brightness profile with a given flux as prescribed by Eq. \ref{flux}, and convolve the PSF profile with a top-hat pixel response with the size of the native scale of the \wfa\ FPA ($p=0.11$ arcseconds per pixel) to produce an effective PSF. 
\item[2.] Draw the effective PSF profile in a noiseless postage stamp of size $1.5k$ by $1.5k$ ($k=64$) pixels at a higher resolution of of $p/N$, with $N=3$, and multiply the resulting image by $N^2$. In this step, NL is not yet applied, but it will be done so in a later step, so the flux still needs to be adjusted. The centroid of the profile is uniformly randomized within the native resolution pixel.
\item[3.] Create another image of the effective PSF at a higher resolution and with the flux adjusted as in step 2. 
Apply the nonlinearity to the postage stamps according to the transformation $I \mapsto I - \beta I^2$ (\emph{c.f.} Eq. \ref{NL}).
\item[4.] Use the adaptive moments algorithm to measure the shape $e_0=(e_{1,0}, e_{2,0})$ and size $R_0$ of the profile without NL to have as baseline reference.
\item[5.] Measure the shape and size of the object with the sensor effect applied, and calculate the quantities $\Delta e_1$, $\Delta e_2$, and $\frac{\Delta R}{R}$, as defined in Eqs. \ref{delta_e} and \ref{delta_r}. 
\item [6.] Repeat steps 1 to 5 %for different AB magnitudes (fluxes) at the nominal value $\beta_0$ and for different $\beta$ values at a fixed magnitude
, averaging over 100 centroid realizations. The values reported will be the mean and the standard deviation over these realizations (see Fig. \ref{f2} and Fig. \ref{f3}).
\item[7.] To study the impact of spatial variability in $\beta$, repeat steps 1 to 6 and assume that the model parameter $\beta$ for each high-resolution pixel can be drawn from a Gaussian distribution with a particular mean $\beta$ and variance $\sigma_{\beta}^2$. Over $M$ realizations (for a fixed centroid), calculate the dispersion values $\sigma_{\Delta e_1}$, $\sigma_{\Delta e_2}$, and $\sigma_{\Delta R/R}$ as a function of $\sigma_{\beta}$. In our simulations we use $M=100$ (see Fig. \ref{f4} and Fig. \ref{f5}).

@@

\begin{figure}[!h]
\centering
\resizebox{\hsize}{!}{\includegraphics[page=1]{plots/f2.eps}}
\caption{Fractional error in PSF size (upper panel) and absolute error in PSF ellipticity components (lower panels) as a function of the mean nonlinearity parameter $\beta$ for the \wfa\ PSF, in four the four HSL filters (J129, Y106, H158, and F184), and an AB magnitude of 18.3 at 168.1 seconds of exposure time. 
Each point is the mean over 100 realizations of uniformly distributed random centroid shifts within the high resolution images ($N=3$).
The standard deviations of the realizations are negligible.}
\label{f2}
\end{figure}

@@

\begin{figure}[!h]
\centering
\resizebox{\hsize}{!}{\includegraphics[page=1]{plots/f3.eps}}
\caption{Fractional error in PSF size and absolute error in PSF ellipticity components normalized by the NL model parameter $\beta$, as a function of magnitude for the four HSL filters (J129, Y106, H158, and F184). The ordinate axis in each plot represents the slope of the linear relationships in Fig. \ref{f2}, derived by linear fitting of points around the vicinity of $\beta_0$ in each curve of that figure.}
\label{f3}
\end{figure}

@@

\begin{figure}[!h]
\centering
\resizebox{\hsize}{!}{\includegraphics[page=1]{plots/f5.eps}}
\caption{Standard deviation of the fractional error in PSF size and of the absolute error in PSF ellipticity components normalized by the error in the NL parameter $\sigma_\beta$, as a function of magnitude for the four HSL filters (J129, Y106, H158, and F184).}
\label{f5}
\end{figure}

>>>>

\documentclass[preprint]{aastex}
%\usepackage{natbib}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{multirow}
%\usepackage{latexsym}
%\usepackage{cancel}
%\usepackage{verbatim}
%\usepackage{indentfirst}
\usepackage{color}

@@

\section{Introduction}
Weak gravitational lensing (WL) has been identified as a powerful probe of the nature and evolution of the components of the Universe. In particular, \emph{cosmic shear}\textemdash the subtle  distortions of background galaxy shapes by the large-scale structure of the Universe\textemdash constrains the properties of dark matter and dark energy through the measurement of the expansion history and growth of structure of the Universe \citep{refregier03, hoekstra08, kilbinger15}. WL measurements also \textcolor{blue}{allows the testing of} the validity of General Relativity that relates the gravitational potential to the matter-energy distribution. Several surveys in the visible part of the spectrum  of $>1000$~deg$^2$ of the sky are currently underway and use the WL signal from hundreds of millions of galaxies as one of their central scientific techniques (\emph{e.g.}, the Dark Energy Survey (DES), \citealt{diehl12}, \citealt{jarvis15}; the Kilo-Degree Survey (KiDS), \citealt{kuijken15}; and the Hyper Suprime-Cam Survey (HSC), \citealt{miyazaki12}). In addition, future ground- and space-based surveys and missions in the visible and near infra-red (NIR) are planned to image more than O($10^9$) galaxies in the next decade (\emph{e.g.}, the Large Synoptic Survey Telescope (LSST), \citealt{ivezic08}; the Euclid spacecraft, \citealt{laureijs11}; and NASA's Wide-Field Infrared Survey Telescope (WFIRST), \citealt{green12}, \citealt{spergel13}, \citealt{spergel15}).

The process of extracting the WL signal from images of the sky, in the presence of intrinsic galaxy ellipticity variations that are $\sim$ 0.4 r.m.s, is highly non-trivial. It must be done through a statistical analysis of large galaxy samples, with a careful control of systematic uncertainties. The dominant signal produced by WL can be described by a local linear transformation of the source image that produces a shear (a complex, spin-2 field of components $\gamma_1$ and $\gamma_2$) and a scalar magnification, both of which have an r.m.s. amplitude of only $\sim 2 \%$ in the case of cosmic shear. Most of the background galaxies usable by WL are at hight redshift (with low signal-to-noise (S/N) ratio) and with a size comparable or smaller than the Point Spread Function (PSF) of the imaging system. Incorrect estimation of the size of the PSF induces a modulation in the signal (multiplicative errors), and errors in the estimation of the PSF ellipticity propagate into asymmetries that produce coherent spurious patterns (additive errors) that mimic the WL signal. Bright stars are commonly used to estimate the PSF, and then this information must be interpolated to the observed galaxy positions to deconvolve the PSF contribution and measure the galaxy shape (in the form of a complex ellipticity $e=e_1 + i e_2$) to estimate the shear field.\footnote{Most of the shape measurement algorithms to date rely on the accurate measurements of galaxy shapes to produce an estimator of the WL shear field $(\gamma_1, \gamma_2)$. However, recent algorithms propose skipping this step and creating a direct shear estimator through Bayesian analysis (\citealt{miller13}, \citealt{bernstein14}, \citealt{bernstein15}, \citealt{schneider15}, \citealt{alsing16}).} This interpolation step introduces systematic errors if the information inferred from the stars does not fully constrain the PSF at the galaxy position with the required accuracy. In order not to bias the determination of dark energy and other cosmological parameters in Stage IV surveys (in the language of \citealt{albrecht06}), the ellipticity and relative size of the PSF must be known to an accuracy of O(10$^{-3}$) (\citealt{huterer06}, \citealt{amara08}, \citealt{paulin08}, \citealt{paulin09}, \citealt{massey13}, \citealt{cropper13}) or better ($4.7 \times 10^{-4}$ for the knowledge of the \wfa\ PSF ellipticity, \citealt{spergel13}).

@@

Systematic errors that originate from a telescope's detectors (image sensors) introduce biases in astronomical observables such as photometry and astrometry that propagate into shear measurement biases. These type of errors have been extensively studied in the case of thick, fully-depleted, high-resistivity Charge Coupled-Devices (CCDs), which are the detectors of choice for many current and planned surveys such as DES, HSC, and LSST (\emph{e.g.}, \citealt{stubbs14}, \citealt{plazas14}, \citealt{gruen15}), \textcolor{blue}{as well as in other types of CCDs (\emph{e.g.}, \citealt{prodhomme14}, \citealt{niemi15}).} It is of great importance to quantify the impact of these sensor effects on the inference of cosmological parameters, in particular through WL (\citealt{jarvis14}, \citealt{mandelbaum14b}, \citealt{meyers14}). Future missions such as the James Webb Space Telescope and \wfa\ will utilize a family of near-infrared detectors that are also subject to effects such as nonlinearity, reciprocity failure (\citealt{bohlin05}, \citealt{biesiadzinski11}), interpixel capacitance (IPC; \citealt{mccullough08}, \citealt{kannawadi15}), and persistence (\citealt{smith08}). These effects can imprint biases on weak lensing shape measurements if not taken into account.

@@

The detector arrays are fabricated with a hybrid complementary metal-oxide-semiconductor (CMOS) architecture, which combines the qualities of HgCdTe to detect infra-red light (\emph{e.g.}, altering the relative molar contributions of mercury and cadmium allows one to tune the band gap \textcolor{blue}{by} up to an order of magnitude) and the advanced readout performance of integrated circuits. Light is absorbed, converted to charge through the photoelectric effect, and collected by electric fields generated by a reverse-biased p-n junction in the detector layer.  The charge per pixel is then converted to a voltage and amplified through a source follower. This operation is performed in the silicon readout integrated circuit (ROIC) layer, which is connected to the HgCdTe detection layer by indium interconnects (one indium bump per pixel). Finally, the ROIC transfers the signal (and for this it is also known as ``multiplexer") to the off-chip electronics at the edge of the FPA, where it is digitized through analog-to-digital converters \citep{beletic08}.

@@

Assuming that the dominant contribution to nonlinearity is the varying capacitance of the pixel p-n junction, the correction to the detector signal is well approximated by a quadratic term:
\begin{align}
S(Q)= Q - \beta Q ^2
\label{NL}
\end{align}
Here, $Q$ is the true number of elementary charges collected in the pixel, $S$ is the number inferred from the voltage change at the sense node, and $\beta$ is a constant.  To estimate $\beta$, we compute $Q(V)=C(V)*V/q_e$, where $q_e$ is the elementary charge, and the total capacitance is given by the varying junction capacitance plus a constant $C(V) = C_{\rm jn}(V) + C_{\rm fix}$. The junction capacitance varies as (\citealt{mccaughrean87})
\begin{equation}
C_{\rm jn}(V) \propto (1+V/V_{bi})^{-1/2} \;.
\end{equation}
Here, $V_{bi}$ is the ``built in'' potential of the junction and $V=V_{\rm DSUB}-V_{\rm RESET}+\delta V$, where $V_{\rm DSUB}$ is the constant potential at the diode cathode, $V_{\rm RESET}$ is the initial potential at the anode, and $\delta V$ is the change in anode potential due to accumulated photocharge.  As an example, we \textcolor{blue}{substitute} measurements of a 2.4$\mu$m cutoff H2RG by Finger 2006:\footnote{\url{https://www.eso.org/sci/meetings/2006/neon-2006/Finger.pdf}}
\begin{eqnarray*}
V_{\rm bi} &=& 0.412\ {\mbox V} \\
V_{\rm DSUB} &=& 1\ {\mbox V} \\
V_{\rm RESET} &=& 0.5\ {\mbox V} \\
C_{\rm fix} &=& 17.8\ {\mbox fF} \\
C_{\rm jn}(V=.912\ {\mbox V}) &=& 30\ {\mbox fF}
\end{eqnarray*}
Using these parameters to compute $Q(V)$ for $ 0\le \delta V \le 0.3$ V (corresponding to maximum $Q$=60115) and then inverting to find $S(Q)$, we find it is well-fit (to 0.1\% or better) by Eq. \ref{NL} with $\beta=1.18 \times 10^{-6}$. In practice, HXRG calibrations have included additional polynomial parameters which can reduce residuals, extend the range of valid $Q$, and account for additional nonlinear effects (\citealt{hilbert04}, \citealt{hilbert08}, \citealt{hilbert14}); however, the additional parameters are highly degenerate, resulting in large variances in the fitted values.  For our purposes, it suffices to analyze the shape-distorting effects of nonlinearity using a single parameter, $\beta$, which encapsulates most of the effect. In this paper we chose a nominal value of $\beta_0=5\times 10^{-7}$, which is near the midpoint of the measured range for $\beta$ in \citealt{hilbert14}.

@@

\citet{kannawadi15} have developed within \gs\ v1.3 a \wfa\ module called ``{\tt{galsim.\\ wfirst}}", which allows the simulation of a PSF profile according to the optical design characteristics of the \wfa\ WFI \citep{pasquale14}\footnote{\citealt{pasquale14} discuss the so-called ``Cycle 4" optical design, whereas the \gs\ \wfa\ module\textemdash used in this work\textemdash uses files corresponding to ``Cycle 5".} through the calling of the {\tt{galsim.wfirst.getPSF}} routine. 
%This routine returns a {\tt{python}} dictionary indexed by each one of the 18 H4RG detectors of the FPA. It uses the optical configuration of the pupil plane\footnote{The pupil plane configuration is not circular in all the bands but the simulated PSFs use circular apertures.} to simulate PSF images in any \wfa\ WFI bandpass filter, with expected optical aberrations approximated as a linear combination of Zernike polynomials (up to Noll order equal to $11$, \citealt{noll67}). 
For this work, we have created simulations in the four bands of the HLS.  A central circular obscuration ($30 \%$; \textcolor{blue}{linear in value}) and six support struts are included as well. %The pupil plane configurations and Zernike models are publicly available.\footnote{\url{http://wfirst.gsfc.nasa.gov/science/sdt_public/wps/references/instrument/}}

%The current version of the module does not include PSF variations across the detector field of view, and the PSF returned corresponds to that at each detector center. In addition, the module assumes that the pupil plane configuration of all the six bands is the same and equivalent to that of the ``red" bands (\emph{i.e.}, W149, H158, and F184), and that the struts are not, in general, radial nor evenly spaced. 
The module generates PSF models that do not include pointing jitter nor charge diffusion. These effects could be added to the profile (\emph{e.g.,} by means of an extra convolution with a Gaussian profile in the case of diffusion), but we did not include them in our simulations. Their effect would be to create a slightly larger PSF, reducing the impact \textcolor{blue}{of} NL. Their omission makes our results slightly conservative.

@@

Note that the NL effect on the reconstructed image from dithering real exposures will depend on the centroid of the source in the dithered inputs: an exposure where the PSF peaks at a pixel center will have higher NL than an exposure where the peak is spread more evenly over 2-4 pixels. To mimic this behavior in our approximation, \textcolor{blue}{we create a PSF profile whose centroid coordinates are random numbers uniformly distributed over the size of a native detector pixel. We then render the profile at a higher resolution $p/N$ and measure its average size and shape over 100 realizations.} With $N$=3, the variation of the NL correction in the pixels of the oversampled image should be similar to the variations in the 5-8 exposures combined using the WFIRST dither strategy.  In practice, we find that the scatters of the shape measurements over these realizations are negligible relative to the means.

@@

Notice that this method to approximate oversampled images can only be used in the case of sensor effects such as NL, which depend on each pixel individually. In the case of other effects that correlate the signal in one pixel with the signal of its neighbors (such as IPC), the effect should be applied to the native scale of the detector and then a properly sampled image should be generated through adequate combination of several dithered images before performing any analysis (see for instance the ``interleaving" algorithm of \citealt{kannawadi15}, also included in \gs).

\begin{figure}[!ht]
\centering
\resizebox{\hsize}{!}{\includegraphics{f1.eps}}
\caption{Example of the \wfa\ PSF profiles in the Y106 band created by the {\tt{galsim.wfirst.getPSF}} method. The profile is drawn on a postage stamp with a size of $1.5k \times1.5k$ pixels ($k=64$) and a resolution of $p/N$, with $p=0.11$ arcseconds and $N=3$. Before drawing the profiles, they are first convolved with a pixel response of size $p$ and given a flux obtained through the use of the {\tt{galsim.wfirst.getBandpasses (AB\char`_zeropoint=True)}} routine at an AB magnitude of 18.3 (at an exposure time of 168.1 seconds). However, to preserve the correct response to NL, the higher-resolution image has $N^2$ more total flux. The NL effect is applied at the high-resolution pixel scale $p/N$, but the centroid of the profile is randomized within the native pixel scale $p$ (in this example the centroid and the pixel center coincide). The upper left panel shows the full postage stamp PSF image without the NL applied, while the lower left panel shows a zoom into the core (squared central region in upper left panel) of 30 by 30 high-resolution pixels. The right-hand side image shows the fractional difference between the PSF without the NL applied and a PSF with NL using $\beta_0$ for the model parameter.} 
\label{f1}
\end{figure}

@@

Total and peak flux values at each filter per postage stamp are shown in Table 1. The brightest magnitude used was AB $m=18.3$, based on the peak value of the PSF profile in the Y106 band when rendered into a postage stamp at the native pixel scale and placed at the center of the pixel: $\sim 1.00237\times10^{5}$ electrons, representing about $90\%$ of the typical full well depth in the pixels of the H4RG detectors\textemdash$\ \sim1.1\times10^{5}$ electrons. Note that this peak value is an upper limit and will vary for a slightly offset profile. \textcolor{blue}{As mentioned before, for each postage stamp in our calculations we select a centroid with random coordinates uniformly distributed within the native scale pixel.} In addition, since NL is a function of signal, and since \gs\ conserves total flux when changing pixel scales, the total flux in the higher resolution image must be multiplied by a factor of $N^2$ to preserve the appropriate response per pixel to this effect, correcting for the fact that the new image has a factor of $N^2$ more pixels than the one created at the native scale.

@@

The basic simulation process is summarized by the following steps:  
\begin{itemize}
\item[1.] Create a \wfa\ PSF surface brightness profile with a given flux as prescribed by Eq. \ref{flux}, and convolve the PSF profile with a top-hat pixel response with the size of the native scale of the \wfa\ FPA ($p=0.11$ arcseconds per pixel) to produce an effective PSF. 
\item[2.] Draw (\textcolor{blue}{\emph{i.e.}, render}) the effective PSF profile in a noiseless postage stamp of size $1.5k$ by $1.5k$ ($k=64$) pixels at a higher resolution of of $p/N$, with $N=3$, and multiply the resulting image by $N^2$. In this step, NL is not yet applied, but it will be done so in a later step, so the flux still needs to be adjusted. \textcolor{blue} {In addition, each coordinate of the PSF centroid is a random number drawn from a uniform distribution within the native resolution pixel.}
\item[3.] Create another image of the effective PSF at a higher resolution and with the flux adjusted as in step 2. 
Apply the nonlinearity to the postage stamps according to the transformation $I \mapsto I - \beta I^2$ (\emph{c.f.} Eq. \ref{NL}).
\item[4.] Use the adaptive moments algorithm to measure the shape $e_0=(e_{1,0}, e_{2,0})$ and size $R_0$ of the profile without NL to have as baseline reference.
\item[5.] Measure the shape and size of the object with the sensor effect applied, and calculate the quantities $\Delta e_1$, $\Delta e_2$, and $\frac{\Delta R}{R}$, as defined in Eqs. \ref{delta_e} and \ref{delta_r}. 
\item [6.] Repeat steps 1 to 5 %for different AB magnitudes (fluxes) at the nominal value $\beta_0$ and for different $\beta$ values at a fixed magnitude
, averaging over 100 centroid realizations. The  \textcolor{blue}{ size and ellipticity} values reported will be the mean and the standard deviation over these realizations (see Fig. \ref{f2} and Fig. \ref{f3}).
\item[7.] To study the impact of spatial variability in $\beta$, repeat steps 1 to 6 and assume that the model parameter $\beta$ for each high-resolution pixel can be drawn from a Gaussian distribution with a particular mean $\beta$ and variance $\sigma_{\beta}^2$. Over $M$ realizations (for a fixed centroid), calculate the dispersion values $\sigma_{\Delta e_1}$, $\sigma_{\Delta e_2}$, and $\sigma_{\Delta R/R}$ as a function of $\sigma_{\beta}$. In our simulations we use $M=100$ (see Fig. \ref{f4} and Fig. \ref{f5}).

@@

\begin{figure}[!h]
\centering
\resizebox{\hsize}{!}{\includegraphics{f2.eps}}
\caption{Fractional error in PSF size (upper panel) and absolute error in PSF ellipticity components (lower panels) as a function of the mean nonlinearity parameter $\beta$ for the \wfa\ PSF, in four the four HSL filters (J129, Y106, H158, and F184), and an AB magnitude of 18.3 at 168.1 seconds of exposure time. 
Each point is the mean over 100 realizations of uniformly distributed random centroid shifts within the high resolution images ($N=3$).
The standard deviations of the realizations are negligible.}
\label{f2}
\end{figure}

@@

\begin{figure}[!h]
\centering
\resizebox{\hsize}{!}{\includegraphics{f3.eps}}
\caption{Fractional error in PSF size and absolute error in PSF ellipticity components normalized by the NL model parameter $\beta$, as a function of magnitude for the four HSL filters (J129, Y106, H158, and F184). The ordinate axis in each plot represents the slope of the linear relationships in Fig. \ref{f2}, derived by linear fitting of points around the vicinity of $\beta_0$ in each curve of that figure.}
\label{f3}
\end{figure}

@@

\begin{figure}[!h]
\centering
\resizebox{\hsize}{!}{\includegraphics{f5.eps}}
\caption{Standard deviation of the fractional error in PSF size and of the absolute error in PSF ellipticity components normalized by the error in the NL parameter $\sigma_\beta$, as a function of magnitude for the four HSL filters (J129, Y106, H158, and F184).}
\label{f5}
\end{figure}
